---
title: "Duke Inference"
author: "Richard Kmieciak"
date: "May 30, 2015"
output: html_document
---
```{r, message=FALSE, warning=FALSE}
load(url("http://s3.amazonaws.com/assets.datacamp.com/course/dasi/inference.Rdata"))
library(openintro);library(dplyr);
```

#Single Mean Estimate  Hypothesis Test
```{r}
a <- rnorm(15, mean = 13, sd = 3)
inference(a,est = "mean", type = "ht", method = "theoretical", null = 15, alternative = "twosided",conflevel = .95)
```

#Single Median Estimate Hypothesis Test
```{r}
a <- rnorm(15, mean = 14, sd = 3)
inference(a,est = "median", type = "ht", method = "simulation", null = 15, alternative = "twosided", conflevel = .95 )
```

#Single Mean Estimate  Confidence Interval
```{r}
a <- rnorm(15, mean = 13, sd = 3)
inference(a,est = "mean", type = "ci", method = "theoretical", boot_method = "se", conflevel = .95 )
```

#Single Median Estimate Confidence Interval
```{r}
a <- rnorm(15, mean = 14, sd = 3)
inference(a,est = "median", type = "ci", method = "simulation", boot_method = "perc", conflevel = .95 )
```


#Two Mean Estimate  Hypothesis Test
```{r}
df <- iris %>% mutate (isSetosa = ifelse(Species == "setosa","yes", "no"))
inference(y = df$Petal.Width,x = df$isSetosa, est = "mean", type = "ht",  method = "theoretical", null = 0,  alternative = "twosided" )
```

#Two Median Estimate  Hypothesis Test
```{r}
df <- iris %>% mutate (isSetosa = ifelse(Species == "setosa","yes", "no"))
inference(y = df$Sepal.Length,x = df$isSetosa, est = "median", type = "ht",  method = "simulation", null = 0,  alternative = "twosided" )
```

#Two Mean Estimate  Confidence Interval
```{r}
df <- iris %>% mutate (isSetosa = ifelse(Species == "setosa","yes", "no"))
inference(y = df$Petal.Width,x = df$isSetosa, est = "mean", type = "ci",  method = "theoretical", conflevel = .95)
```

#Two Median Estimate  Confidence Interval
```{r}
df <- iris %>% mutate (isSetosa = ifelse(Species == "setosa","yes", "no"))
inference(y = df$Sepal.Length,x = df$isSetosa, est = "median", type = "ci",  method = "simulation", boot_method = "perc")
```


#Anova Mean differ across categorical groups? Hypothesis test.
```{r}
df <- mtcars %>% mutate (cyl = factor(cyl))
inference(y = df$mpg,x = df$cyl, est = "mean", type = "ht",  method = "theoretical", alternative = "greater")
```




